---
title: "main-functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{main-functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(measlr)
```

```{r}
mean_measles_per_month_for_countr(measles_data, country)
```
This should make a table for a specific country that outputs the mean measles incidence rate for each month, as well as the standard deviation,

```{r}
mean_measles_by_country(measles_data, urban_data, countries)
```
Takes a list of countries and creates a lollipop graph of each countries mean incidence rate. Then, the function adds a horizontal line corresponding to the overall mean measles incidence rate for each urban classification present in the list of countries.

```{r}
prepare_urban_pop_data(measles_data, urban_data)
```
Reads in a data set with urban populations, then combines it with the original measles data set. It then adds a column containing each countries urban classification. 
