---
title: "main-functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{main-functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(measlr)
```

```{r}
mean_measles_per_month_for_country(measles_data, country_nam = "United States")
```
This should make a table for a specific country that outputs the mean measles incidence rate for each month, as well as the standard deviation.

```{r}
mean_measles_by_country(countries)
```
Takes a list of countries and creates a lollipop graph of each countries mean incidence rate. Then, the function adds a horizontal line corresponding to the overall mean measles incidence rate for each urban classification present in the list of countries.

```{r}
prepare_mean_measles_data(urban_data, countries)
```
Filters the urban–measles data set to the selected countries, then computes mean measles incidence by country and by urban classification and returns a data frame to be used for plotting

```{r}
country_plot(country_name)
```
Takes one country and makes a bar graph of that country's measles cases per month. 

```{r}
country_incidence_summary("USA")
```
Summarizes measles incidence rate for the selected country from ISO3 code. The output includes the country's urban classification and the mean and standard deviation measles incidence rate per 1,000,000 population
